---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countMissingWyatt

This package provides tools for analyzing and summarizing missing data across groups in a dataset. It includes functions to group data by a specified column and count the number of missing values in each column within each group, simplifying data quality assessments.

## Student Info

name: Xiang Zhang 

## Installation

You can install the development version of this package from GitHub:

```{r}
devtools::install_github("stat545ubc-2024/countMissingWyatt", ref = "0.1.1")
```

## Usage

Load the package and use `count_all_missing_by_group()` to analyze missing values in grouped data. Here’s an example with the `airquality` dataset:

```{r}
library(countMissingWyatt)
data(airquality)
# Count missing values grouped by Month
count_all_missing_by_group(airquality, Month)


#To keep the output grouped by the grouping column, use the .groups argument:

count_all_missing_by_group(airquality, Month, .groups = "keep")
```
